### 2013-11-10 Article/book/BookSources/chapter3SimpleRules.tex
changed: figures potition

\chapter{Znaczenie prostych zasad w strategiach inwestycyjnych handlu algorytmicznego}
\label{SimpleRules} % Always give a unique label
% use \chaptermark{}
% to alter or adjust the chapter heading in the running head
\section{abstract}
\label{sec:c3abstract}
% Always give a unique label % and use \ref{<label>} for cross-references % and \cite{<label>} for bibliographic references % use \sectionmark{} to alter or adjust the section heading in the running head
In article are shown studies of the possibly simplest investment strategy of algo trading. The authors' intention was to prove the thesis that in the greedy algorithmic trading directed to the proper response, not to forecast, there are almost always opportunities to achieve profit. This paper presents the results of tests for over twenty core markets - currency pairs, indices and commodities (eight results included). Introduced the original concept of quadrant of openings on each bar. In principle, the strategy is not relevant investment (studies were conducted without transaction costs), only cognitive in order to develop.

@@

\section{The test results}
\label{sec:c3TheTestResults}
\indent The charts below show the curves of capital accumulation for each quarter of quadrant. Each graph represents one decision-making situation with the best parameter, number of last closures to calculate moving average. Fifth diagram shows the (S1s) cumulative strategy value, which is the sum of profit of all open positions at this moment. Obviously all component strategies are calculated for the best parameter for each one of them.\\
\indent Following tables present the results of conducted simulations aimed at finding the best number of bars required to calculate means (bestMALength). Column "strategy" specifies which strategy was used, "profit" - the cumulative sum of the profit. Third column, "bestCalmar", represents Calmar Ratio which describes profit-to-maximum drawdown ratio. Low Calmar Ratio indicates poor investment performance on a risk-adjusted basis during certain time span. Last column "la" presents the number of open positions.
The study of strategy was carried out on the following markets:
\begin{itemize}
\item currency pairs: EURJPY, USDJPY, GBPUSD, EURUSD,
\item indices: FUS500, BOSSAPLN,
\item commodities: FGOLD. FSILVER.
\end{itemize}
BOSSAPLN is currency index that represents ratio of PLN to four other currencies. Every currency pair used to calculate index has other weight USDPLN (40\%), EURPLN (50\%), GBPPLN (5\%), CHFPLN (5\%).
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for EURJPY} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 26.18 & 5.59 & 24 & 2764\\ \hline 
S1b & -14.77 & -0.67 & 6 & 2660\\ \hline 
S1c & 15.74 & 2.49 & 6 & 2332\\ \hline 
S1d & -4.57 & -0.47 & 21 & 2226\\ \hline 
S1s & 22.54 & 3.25 & Group of MA & 4975\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

\begin{figure}[h]
\centering
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1a_eurjpy.eps}
\subcaption{Profit - S1a}
\label{jedno}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1b_eurjpy.eps}
\subcaption{Profit - S1b}
\label{dwu}
\end{minipage}
\\
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1c_eurjpy.eps}
\subcaption{Profit- S1c}
\label{cztero}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1d_eurjpy.eps}
\subcaption{Profit - S1d}
\label{mansard}
\end{minipage}
\begin{minipage}{\linewidth}
\centering 
\includegraphics[width=0.6\textwidth]{images/S1s_eurjpy.eps}
\label{mansard}
\subcaption{Profit - S1s}
\end{minipage}
\caption{EURJPY market results}
\end{figure}
\FloatBarrier
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for USDJPY} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline 
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline 
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline 
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline 
S1s & 14.85 & 5.68 & Group of MA & 4945\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

\begin{figure}[h]
\centering
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1a_usdjpy.eps}
\subcaption{Profit - S1a}
\label{jedno}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1b_usdjpy.eps}
\subcaption{Profit - S1b}
\label{dwu}
\end{minipage}
\\
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1c_usdjpy.eps}
\subcaption{Profit- S1c}
\label{cztero}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1d_usdjpy.eps}
\subcaption{Profit - S1d}
\label{mansard}
\end{minipage}
\begin{minipage}{\linewidth}
\centering 
\includegraphics[width=0.6\textwidth]{images/S1s_usdjpy.eps}
\label{mansard}
\subcaption{Profit - S1s}
\end{minipage}
\caption{USDJPY market results}
\end{figure}
\FloatBarrier

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for GBPUSD} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 0.06 & 1.06 & 92 & 2588\\ \hline 
S1b & 0.12 & 3.41 & 5 & 2513\\ \hline 
S1c & 0.15 & 3.11 & 5 & 2475\\ \hline 
S1d & 0.02 & 0.31 & 92 & 2319\\ \hline 
S1s & 0.36 & 6.89 & Group of MA & 4907\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

\begin{figure}[h]
\centering
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1a_gbpusd.eps}
\subcaption{Profit - S1a}
\label{jedno}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1b_gbpusd.eps}
\subcaption{Profit - S1b}
\label{dwu}
\end{minipage}
\\
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1c_gbpusd.eps}
\subcaption{Profit- S1c}
\label{cztero}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1d_gbpusd.eps}
\subcaption{Profit - S1d}
\label{mansard}
\end{minipage}
\begin{minipage}{\linewidth}
\centering 
\includegraphics[width=0.6\textwidth]{images/S1s_gbpusd.eps}
\label{mansard}
\subcaption{Profit - S1s}
\end{minipage}
\caption{GBPUSD market results}
\end{figure}
\FloatBarrier

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for EURUSD} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 0.09 & 1.84 & 33 & 2635\\ \hline 
S1b & 0.01 & 0.16 & 5 & 2587\\ \hline 
S1c & 0.12 & 3.45 & 5 & 2406\\ \hline 
S1d & -0.02 & -0.49 & 33 & 2331\\ \hline 
S1s & 0.21 & 3.31 & Group of MA & 4966\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

\begin{figure}[h]
\centering
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1a_eurusd.eps}
\subcaption{Profit - S1a}
\label{jedno}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1b_eurusd.eps}
\subcaption{Profit - S1b}
\label{dwu}
\end{minipage}
\\
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1c_eurusd.eps}
\subcaption{Profit- S1c}
\label{cztero}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1d_eurusd.eps}
\subcaption{Profit - S1d}
\label{mansard}
\end{minipage}
\begin{minipage}{\linewidth}
\centering 
\includegraphics[width=0.6\textwidth]{images/S1s_eurusd.eps}
\label{mansard}
\subcaption{Profit - S1s}
\end{minipage}
\caption{EURUSD market results}
\end{figure}
\FloatBarrier

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for FUS500} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 274.89 & 5.44 & 83 & 3200\\ \hline 
S1b & -70.94 & -0.47 & 15 & 2798\\ \hline 
S1c & 291.62 & 4.26 & 15 & 2186\\ \hline 
S1d & -106.67 & -0.73 & 82 & 1723\\ \hline 
S1s & 344.29 & 2.08 & Group of MA & 4916\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

\begin{figure}[h]
\centering
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1a_fus.eps}
\subcaption{Profit - S1a}
\label{jedno}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1b_fus.eps}
\subcaption{Profit - S1b}
\label{dwu}
\end{minipage}
\\
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1c_fus.eps}
\subcaption{Profit- S1c}
\label{cztero}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1d_fus.eps}
\subcaption{Profit - S1d}
\label{mansard}
\end{minipage}
\begin{minipage}{\linewidth}
\centering 
\includegraphics[width=0.6\textwidth]{images/S1s_fus.eps}
\label{mansard}
\subcaption{Profit - S1s}
\end{minipage}
\caption{FUS500 market results}
\end{figure}
\FloatBarrier

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for BOSSAPLN} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 5.87 & 1.99 & 21 & 2474\\ \hline 
S1b & 2.86 & 0.61 & 5 & 2416\\ \hline 
S1c & 10.91 & 4.33 & 5 & 2547\\ \hline 
S1d & -2.23 & -0.42 & 21 & 2502\\ \hline 
S1s & 17.91 & 4.35 & Group of MA & 4978\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

\begin{figure}[h]
\centering
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1a_bossa.eps}
\subcaption{Profit - S1a}
\label{jedno}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1b_bossa.eps}
\subcaption{Profit - S1b}
\label{dwu}
\end{minipage}
\\
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1c_bossa.eps}
\subcaption{Profit- S1c}
\label{cztero}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1d_bossa.eps}
\subcaption{Profit - S1d}
\label{mansard}
\end{minipage}
\begin{minipage}{\linewidth}
\centering 
\includegraphics[width=0.6\textwidth]{images/S1s_bossa.eps}
\label{mansard}
\subcaption{Profit - S1s}
\end{minipage}
\caption{BOSSAPLN market results}
\end{figure}
\FloatBarrier

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for FGOLD} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 61.16 & 0.59 & 51 & 2578\\ \hline 
S1b & 227.58 & 2.82 & 5 & 2519\\ \hline 
S1c & 30.38 & 0.12 & 5 & 2470\\ \hline 
S1d & 248.21 & 1.52 & 51 & 2370\\ \hline 
S1s & 599.88 & 4.60 & Group of MA & 4948\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

\begin{figure}[h]
\centering
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1a_gold.eps}
\subcaption{Profit - S1a}
\label{jedno}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1b_gold.eps}
\subcaption{Profit - S1b}
\label{dwu}
\end{minipage}
\\
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1c_gold.eps}
\subcaption{Profit- S1c}
\label{cztero}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1d_gold.eps}
\subcaption{Profit - S1d}
\label{mansard}
\end{minipage}
\begin{minipage}{\linewidth}
\centering 
\includegraphics[width=0.6\textwidth]{images/S1s_gold.eps}
\label{mansard}
\subcaption{Profit - S1s}
\end{minipage}
\caption{FGOLD market results}
\end{figure}
\FloatBarrier

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for FSILVER} 
\begin{center}
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & -5.31 & -0.65 & 81 & 2582\\ \hline 
S1b & 17.22 & 5.86 & 10 & 2508\\ \hline 
S1c & 4.17 & 0.56 & 10 & 2473\\ \hline 
S1d & 6.95 & 1.33 & 81 & 2336\\ \hline 
S1s & 21.96 & 5.55 & Group of MA & 4918\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

\begin{figure}[h]
\centering
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1a_silver.eps}
\subcaption{Profit - S1a}
\label{jedno}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1b_silver.eps}
\subcaption{Profit - S1b}
\label{dwu}
\end{minipage}
\\
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1c_silver.eps}
\subcaption{Profit- S1c}
\label{cztero}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1d_silver.eps}
\subcaption{Profit - S1d}
\label{mansard}
\end{minipage}
\begin{minipage}{\linewidth}
\centering 
\includegraphics[width=0.6\textwidth]{images/S1s_silver.eps}
\label{mansard}
\subcaption{Profit - S1s}
\end{minipage}
\caption{FSILVER market results}
\end{figure}
\FloatBarrier

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for CADCHF}
 \begin{center}
 \begin{tabular}{|l|l|l|l|l|}
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
S1s & 14.85 & 5.68 & Group of MA & 4945\\
\hline \end{tabular}
 \end{center}
 \end{table}
\FloatBarrier

\begin{figure}[h]
\centering
\begin{minipage}{.49\linewidth}
\centering
\includegraphics[width=0.82\textwidth]{images/cadchfS1a.eps}
\subcaption{Profit - S1a}
\label{jedno}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering
\includegraphics[width=0.82\textwidth]{images/cadchfS1b.eps}
\subcaption{Profit - S1b}
\label{dwu}
\end{minipage}
\\
\begin{minipage}{.49\linewidth}
\centering
\includegraphics[width=0.82\textwidth]{images/cadchfS1c.eps}
\subcaption{Profit - S1c}
\label{cztero}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering
\includegraphics[width=0.82\textwidth]{images/cadchfS1d.eps}
\subcaption{Profit - S1d}
\label{mansard}
\end{minipage}
\begin{minipage}{\linewidth}
\centering
\includegraphics[width=0.6\textwidth]{images/cadchfS1s.eps}
\label{mansard}
\subcaption{Profit - S1s}
\end{minipage}
\caption{CADCHF market results}
\end{figure}
\FloatBarrier

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{table}[!t]
\caption{Profits for all strategy quadrants for FCOPPER}
 \begin{center}
 \begin{tabular}{|l|l|l|l|l|}
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
S1s & 14.85 & 5.68 & Group of MA & 4945\\
\hline \end{tabular}
 \end{center}
 \end{table}
\includegraphics[width=0.82\textwidth]{images/fcopperS1a.eps}
\subcaption{Profit - S1a}
\includegraphics[width=0.82\textwidth]{images/fcopperS1b.eps}
\subcaption{Profit - S1b}
\includegraphics[width=0.82\textwidth]{images/fcopperS1c.eps}
\subcaption{Profit - S1c}
\includegraphics[width=0.82\textwidth]{images/fcopperS1d.eps}
\subcaption{Profit - S1d}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/fcopperS1s.eps}
\subcaption{Profit - S1s}
\caption{FCOPPER market results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\caption{Profits for all strategy quadrants for FCORN}
 \begin{center}
 \begin{tabular}{|l|l|l|l|l|}
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
S1s & 14.85 & 5.68 & Group of MA & 4945\\
\hline \end{tabular}
 \end{center}
 \end{table}
\includegraphics[width=0.82\textwidth]{images/fcornS1a.eps}
\subcaption{Profit - S1a}
\includegraphics[width=0.82\textwidth]{images/fcornS1b.eps}
\subcaption{Profit - S1b}
\includegraphics[width=0.82\textwidth]{images/fcornS1c.eps}
\subcaption{Profit - S1c}
\includegraphics[width=0.82\textwidth]{images/fcornS1d.eps}
\subcaption{Profit - S1d}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/fcornS1s.eps}
\subcaption{Profit - S1s}
\caption{FCORN market results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\caption{Profits for all strategy quadrants for NZDJPY}
 \begin{center}
 \begin{tabular}{|l|l|l|l|l|}
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
S1s & 14.85 & 5.68 & Group of MA & 4945\\
\hline \end{tabular}
 \end{center}
 \end{table}
\includegraphics[width=0.82\textwidth]{images/nzdjpyS1a.eps}
\subcaption{Profit - S1a}
\includegraphics[width=0.82\textwidth]{images/nzdjpyS1b.eps}
\subcaption{Profit - S1b}
\includegraphics[width=0.82\textwidth]{images/nzdjpyS1c.eps}
\subcaption{Profit - S1c}
\includegraphics[width=0.82\textwidth]{images/nzdjpyS1d.eps}
\subcaption{Profit - S1d}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/nzdjpyS1s.eps}
\subcaption{Profit - S1s}
\caption{NZDJPY market results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\caption{Profits for all strategy quadrants for USDCAD}
 \begin{center}
 \begin{tabular}{|l|l|l|l|l|}
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
S1s & 14.85 & 5.68 & Group of MA & 4945\\
\hline \end{tabular}
 \end{center}
 \end{table}
\includegraphics[width=0.82\textwidth]{images/usdcadS1a.eps}
\subcaption{Profit - S1a}
\includegraphics[width=0.82\textwidth]{images/usdcadS1b.eps}
\subcaption{Profit - S1b}
\includegraphics[width=0.82\textwidth]{images/usdcadS1c.eps}
\subcaption{Profit - S1c}
\includegraphics[width=0.82\textwidth]{images/usdcadS1d.eps}
\subcaption{Profit - S1d}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/usdcadS1s.eps}
\subcaption{Profit - S1s}
\caption{USDCAD market results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\caption{Profits for all strategy quadrants for CHFJPY}
 \begin{center}
 \begin{tabular}{|l|l|l|l|l|}
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
S1s & 14.85 & 5.68 & Group of MA & 4945\\
\hline \end{tabular}
 \end{center}
 \end{table}
\includegraphics[width=0.82\textwidth]{images/chfjpyA.eps}
\subcaption{Profit - pyA}
\includegraphics[width=0.82\textwidth]{images/chfjpyB.eps}
\subcaption{Profit - pyB}

>>>>

\chapter{Znaczenie prostych zasad w strategiach inwestycyjnych handlu algorytmicznego}
\label{SimpleRules} % Always give a unique label
% use \chaptermark{}
% to alter or adjust the chapter heading in the running head

%\label{sec:c3abstract}
% Always give a unique label % and use \ref{<label>} for cross-references % and \cite{<label>} for bibliographic references % use \sectionmark{} to alter or adjust the section heading in the running head
In article are shown studies of the possibly simplest investment strategy of algo trading. The authors' intention was to prove the thesis that in the greedy algorithmic trading directed to the proper response, not to forecast, there are almost always opportunities to achieve profit. This paper presents the results of tests for over twenty core markets - currency pairs, indices and commodities (eight results included). Introduced the original concept of quadrant of openings on each bar. In principle, the strategy is not relevant investment (studies were conducted without transaction costs), only cognitive in order to develop.

@@

\section{The test results}
\label{sec:c3TheTestResults}
\indent The charts below show the curves of capital accumulation for each quarter of quadrant. Each graph represents one decision-making situation with the best parameter, number of last closures to calculate moving average. Fifth diagram shows the (S1s) cumulative strategy value, which is the sum of profit of all open positions at this moment. Obviously all component strategies are calculated for the best parameter for each one of them.\\
\indent Following tables present the results of conducted simulations aimed at finding the best number of bars required to calculate means (bestMALength). Column "strategy" specifies which strategy was used, "profit" - the cumulative sum of the profit. Third column, "bestCalmar", represents Calmar Ratio which describes profit-to-maximum drawdown ratio. Low Calmar Ratio indicates poor investment performance on a risk-adjusted basis during certain time span. Last column "la" presents the number of open positions.
The study of strategy was carried out on the following markets:
\begin{itemize}
\item currency pairs: EURJPY, USDJPY, GBPUSD, EURUSD,
\item indices: FUS500, BOSSAPLN,
\item commodities: FGOLD. FSILVER.
\end{itemize}
BOSSAPLN is currency index that represents ratio of PLN to four other currencies. Every currency pair used to calculate index has other weight USDPLN (40\%), EURPLN (50\%), GBPPLN (5\%), CHFPLN (5\%).

@@

%\begin{table}[!t]
%\caption{Profits for all strategy quadrants for EURJPY} 
% \begin{center} 
% \begin{tabular}{|l|l|l|l|l|} 
% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
%S1a & 26.18 & 5.59 & 24 & 2764\\ \hline 
%S1b & -14.77 & -0.67 & 6 & 2660\\ \hline 
%S1c & 15.74 & 2.49 & 6 & 2332\\ \hline 
%S1d & -4.57 & -0.47 & 21 & 2226\\ \hline 
%S1s & 22.54 & 3.25 & Group of MA & 4975\\ 
%\hline \end{tabular} 
% \end{center} 
% \end{table}
%\FloatBarrier
%
%\begin{figure}[h]
%\centering
%\begin{minipage}{.49\linewidth}
%\centering 
%\includegraphics[width=0.82\textwidth]{images/S1a_eurjpy.eps}
%\subcaption{Profit - S1a}
%\label{jedno}
%\end{minipage}
%\begin{minipage}{.49\linewidth}
%\centering 
%\includegraphics[width=0.82\textwidth]{images/S1b_eurjpy.eps}
%\subcaption{Profit - S1b}
%\label{dwu}
%\end{minipage}
%\\
%\begin{minipage}{.49\linewidth}
%\centering 
%\includegraphics[width=0.82\textwidth]{images/S1c_eurjpy.eps}
%\subcaption{Profit- S1c}
%\label{cztero}
%\end{minipage}
%\begin{minipage}{.49\linewidth}
%\centering 
%\includegraphics[width=0.82\textwidth]{images/S1d_eurjpy.eps}
%\subcaption{Profit - S1d}
%\label{mansard}
%\end{minipage}
%\begin{minipage}{\linewidth}
%\centering 
%\includegraphics[width=0.6\textwidth]{images/S1s_eurjpy.eps}
%\label{mansard}
%\subcaption{Profit - S1s}
%\end{minipage}
%\caption{EURJPY market results}
%\end{figure}
%\FloatBarrier
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage
%\begin{table}[!t]
%\caption{Profits for all strategy quadrants for USDJPY} 
% \begin{center} 
% \begin{tabular}{|l|l|l|l|l|} 
% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
%S1a & 17.19 & 8.24 & 18 & 2693\\ \hline 
%S1b & -9.80 & -0.74 & 54 & 2665\\ \hline 
%S1c & 5.65 & 2.06 & 54 & 2280\\ \hline 
%S1d & 1.87 & 0.61 & 18 & 2287\\ \hline 
%S1s & 14.85 & 5.68 & Group of MA & 4945\\ 
%\hline \end{tabular} 
% \end{center} 
% \end{table}
%\FloatBarrier
%
%\begin{figure}[h]
%\centering
%\begin{minipage}{.49\linewidth}
%\centering 
%\includegraphics[width=0.82\textwidth]{images/S1a_usdjpy.eps}
%\subcaption{Profit - S1a}
%\label{jedno}
%\end{minipage}
%\begin{minipage}{.49\linewidth}
%\centering 
%\includegraphics[width=0.82\textwidth]{images/S1b_usdjpy.eps}
%\subcaption{Profit - S1b}
%\label{dwu}
%\end{minipage}
%\\
%\begin{minipage}{.49\linewidth}
%\centering 
%\includegraphics[width=0.82\textwidth]{images/S1c_usdjpy.eps}
%\subcaption{Profit- S1c}
%\label{cztero}
%\end{minipage}
%\begin{minipage}{.49\linewidth}
%\centering 
%\includegraphics[width=0.82\textwidth]{images/S1d_usdjpy.eps}
%\subcaption{Profit - S1d}
%\label{mansard}
%\end{minipage}
%\begin{minipage}{\linewidth}
%\centering 
%\includegraphics[width=0.6\textwidth]{images/S1s_usdjpy.eps}
%\label{mansard}
%\subcaption{Profit - S1s}
%\end{minipage}
%\caption{USDJPY market results}
%\end{figure}
%\FloatBarrier
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage
%\begin{table}[!t]
%\caption{Profits for all strategy quadrants for GBPUSD} 
% \begin{center} 
% \begin{tabular}{|l|l|l|l|l|} 
% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
%S1a & 0.06 & 1.06 & 92 & 2588\\ \hline 
%S1b & 0.12 & 3.41 & 5 & 2513\\ \hline 
%S1c & 0.15 & 3.11 & 5 & 2475\\ \hline 
%S1d & 0.02 & 0.31 & 92 & 2319\\ \hline 
%S1s & 0.36 & 6.89 & Group of MA & 4907\\ 
%\hline \end{tabular} 
% \end{center} 
% \end{table}
%\FloatBarrier
%
%\begin{figure}[h]
%\centering
%\begin{minipage}{.49\linewidth}
%\centering 
%\includegraphics[width=0.82\textwidth]{images/S1a_gbpusd.eps}
%\subcaption{Profit - S1a}
%\label{jedno}
%\end{minipage}
%\begin{minipage}{.49\linewidth}
%\centering 
%\includegraphics[width=0.82\textwidth]{images/S1b_gbpusd.eps}
%\subcaption{Profit - S1b}
%\label{dwu}
%\end{minipage}
%\\
%\begin{minipage}{.49\linewidth}
%\centering 
%\includegraphics[width=0.82\textwidth]{images/S1c_gbpusd.eps}
%\subcaption{Profit- S1c}
%\label{cztero}
%\end{minipage}
%\begin{minipage}{.49\linewidth}
%\centering 
%\includegraphics[width=0.82\textwidth]{images/S1d_gbpusd.eps}
%\subcaption{Profit - S1d}
%\label{mansard}
%\end{minipage}
%\begin{minipage}{\linewidth}
%\centering 
%\includegraphics[width=0.6\textwidth]{images/S1s_gbpusd.eps}
%\label{mansard}
%\subcaption{Profit - S1s}
%\end{minipage}
%\caption{GBPUSD market results}
%\end{figure}
%\FloatBarrier
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage
%\begin{table}[!t]
%\caption{Profits for all strategy quadrants for EURUSD} 
% \begin{center} 
% \begin{tabular}{|l|l|l|l|l|} 
% \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
